\section{Data And Methodology}
\label{sec:data_and_methodology}

In this section I overview the data sources used, any preprocessing and sanity
checks I performed, and the methodology used to perform the econometric
analysis.

\subsection{Data Sources}

Two major sources:
\begin{enumerate}
\item The International Telecommunication Union World Telecommunication Indicators
Database, from 2001-2011~\cite{itu}.
\item The World Bank World Development Indicators Online Database, from
1980-2011~\cite{wdi}.
\end{enumerate}

Any touching up / sanity checking I needed to do to the data

Some processing on names was needed to canonacalize across the two datasets.

NOTE: see scripts/README for additional notes on data analysis

- Country classifications are taken from the World
Bank. http://data.worldbank.org/income-level/NOC
TODO: Citation

The code used to perform this analysis is publicly available~\cite{github}.

\subsection{Methodology}

Econometric regression over 6 variables.
Across 120 countries.
Bucketed into low/middle/high income.

Dependent variable: GDP.

Independent variables:
\begin{enumerate}
\item Average broadband penetration per 100 people.
\item GDP per capita in 1980.
\item Ratio of gross investment to GDP.
\item Primary school enrollment (human capital).
\item Dummy variable for countries in Sub-Saharan Africa
\item Dummy variable for countries in Latin America / Caribbean
\end{enumerate}

These variables were chosen based on an Endogenous Growth Model.
Explain all the things I learned about growth models (why I didn't use an
exogenous model, etc.)

Fancy math equation for endogenous growth.
